Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-11-05 Draft/draft.tex
Honghao: arXiv version 1

\author{Honghao Fu
\footnote{\href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}

@@

\date{}
\affil{Department of Computer Science, Institute for Advanced Computer Studies, and Joint Center for Quantum \break Information and Computer Science, University of Maryland, College Park, MD 20742, USA
\break
}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generators
	are at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

@@

The fact that the verifier only interacts classically with the unknown device
makes self-testing a powerful tool 
for applications in 
quantum cryptography and computational
complexity theory.
It allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
It also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,vv2014,fu2018}.
Since the setting of multi-prover interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

@@

Our work aims at minimizing the sizes of the input 
and output alphabets of a correlation that can self-test
a maximally entangled states with large local dimension.
% that are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
Our progress is summarized in the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

@@

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that the sizes of the input or output alphabet of $\fC(d,r)$ is independent of $d$. 
% the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment to each variable of the equation.
Bob is asked to assign a value to a random variable of that equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of $\ket{EPR}$
the Magic square game can be won with certainty.
It has been shown that if a strategy that can win this game almost perfectly, 
the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain binary observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation \cite{coladan2017}.

@@

Following Slofstra's design, 
the game $\LS(r)$ is constructed so that the sizes
of the input alphabets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
$\LS(r)$ only uses constant-sized input and output alphabets.

The reason that we choose \cref{eq:uor} to be the relation enforced
by $\LS(r)$ is the following.
Winning $\LS(r)$ implies that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2
\end{align*}
with $U$ and $O$ satisfying \cref{eq:uor}.
Then we can deduce that the eigenvalues of $O$ must be
of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game also implies that Alice and Bob share a state
$\ket{\psi}$ such that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$,
and is invariant under the permutation induced by $U$
% \begin{align*}
%     O \x O \ket{\psi} = \ket{\psi}, && 
%     U \x U \ket{\psi} = \ket{\psi}.
% \end{align*}
% The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
% is spanned by tensor products of states in the eigenbasis of $O$.
% The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
% under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
certifying the eigenvalues of $O$ requires another test.

@@

The remaining question is how to certify eigenvalues of $O$, so we
design a nonlocal test called the extended weighted CHSH test.
% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
The combination of a linear system game with 
a nonlocal test in the construction of $\fC(d,r)$ 
is a new way to use a linear system game for robust self-testing.
It distinguishes our approach from all the previous ones.

The extended weighted CHSH test is designed based on the $\alpha$-weighted CHSH inequality, 
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    \tM_1 = \pauliz && \tM_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    \tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && \tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $\tM_1, \tM_2$ and $\tN_1, \tN_2$ in \cref{sec:ext_chsh}.
Then we notice that 
\begin{align*}
    \tN_1\tN_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.

Therefore, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$ defined in $\LS(r)$. Then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
and the eigenspaces of all the eigenvalues have the same cardinality.

At this point, we have the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$,
\begin{align*}
    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
    \ket{EPR}^{\x 2}.
\end{align*}
In this proof, we demonstrate a new way to apply the generalized swap-isometry
proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
dimension.

Our contributions are:
\begin{enumerate}
\item We identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
maximally entangled states with unbounded local dimensions. Before our work, the most efficient way 
was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.

\item Our result gives us deeper understandings of the set of quantum correlations.
In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
lower bounds of the entanglement required to achieve certain correlations are identified.
We discover a large family of correlations such that we know exactly the entangled state
required to achieve each of the correlations in this family. 
\end{enumerate}

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:ext_chsh}. 
Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
In the end, we give the robust self-testing proof in \cref{sec:main}.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations and mathematical background}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$.

In the qubit case, the EPR pair is denoted by 
\begin{align}
	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are denoted by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}
Note that we only work with finite Hilbert spaces in our work.

@@

There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
\begin{definition}
    \label{def:spe_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let
    \begin{align*}
        \Gamma = \ip{\{s_i\}_{i \in [n]}  :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{ s_i s_j s_i = s_k\}_{(i,j,k)\in C}}.
    \end{align*}
    We say a group is a conjugacy group if it has a presentation of this form. 
\end{definition}
A conjugacy group is a special case of what Slofstra defined as 
a linear-plus-conjugacy group (Definition $26$ of \cite{slofstra2017}). 
The difference is that a conjugacy group does not have linear relations. 
The next definition follows the 
definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
\begin{definition}
    \label{def:nice_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let 
    \begin{align*}
        \Gamma = \ip{\{s_i\}_{i \in [n]} \cup \{s_{jk}\}_{(i,j,k)\in C} :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{s_{jk}^2 = e, s_is_js_i = s_k, s_{jk}s_js_k = e\}_{(i,j,k)\in C}}.
    \end{align*}
    We say a group is a nice conjugacy group if it has a presentation of this form. 
\end{definition}
The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
because
\begin{align*}
    [s_j, s_k] = s_js_ks_js_k = s_{jk}^2 = e.
\end{align*}

Next we give the definition of a group representation. 
\begin{definition}
    A representation of a group $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
\end{definition}
The last concept of group theory that we need is a group embedding.
\begin{definition}[Group embedding]
    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
\end{definition}
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. 
We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
for each $x \in \calX$. Similarly,
Bob's question set is denoted by $\calY$ and 
his family of answer sets is denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, 
and we follow this convention on Bob's side too.
The probability distribution over the questions of
a nonlocal game 
is given by a functions $\pi: \calX \times \calY \rightarrow [0,1]$,
A nonlocal game also comes with a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
the family of scoring functions.
Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the scoring function as 
$V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.

@@

>>>>

\author{Honghao Fu
\footnote{Email: \href{mailto:h7fu@umd.edu}{h7fu@umd.edu}}}

@@

\date{}
\affil{
Joint Center for Quantum Information and Computer Science, \break
Institute for Advanced Computer Studies and Department of Computer Science,\break 
University of Maryland, College Park, MD 20742, USA
}
%\affil[2]{National Institute of Standards and Technology, 100 Bureau Dr., Gaithersbug, MD 20899, USA}
\maketitle

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generator
	is at most $5$ (M. Murty \textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

@@

The fact that the verifier only interacts classically with the unknown device
makes self-testing a powerful tool 
for applications in 
quantum cryptography and computational
complexity theory.
It allows a classical party to delegate quantum computations to some untrusted service provider
and verify that the computations are performed
honestly and correctly \cite{ruv2013,coladan2017verifier}.
Self-testing also becomes a critical component of the security proofs of device-independent quantum cryptographic protocols
\cite{mayersyao,fu2018}.
Since the setting of multi-prover interactive proof systems is similar to a self-test, self-testing arguments also help to prove
lower bounds of the computational power of entanglement-assisted
multiprover interactive proof systems \cite{fitzsimons2019, neexp}.

@@

Our work aims at minimizing the sizes of the input 
and output alphabets of a correlation that can self-test
a maximally entangled states with large local dimension.
% that are independent of the local dimension of the self-tested state.
For comparisons, all the correlations used in the results listed above
have either input or output alphabets with sizes dependent on the
local dimension of the entangled state.
Our progress is summarized in the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized input and output alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

@@

To prove \cref{thm:inf}, we construct a correlation with $\Theta(r)$-sized
input and constant-sized output alphabets
for each odd prime number $d$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that the size of neither the input nor the output alphabet of $\fC(d,r)$ depends on $d$. 
% the distributions in $\fC(d,r)$ do. 
Once we prove $\fC(d,r)$ can robustly self-test a maximally entangled
state of dimension $4(d-1)$, we apply it to all $d \in D$
and prove \cref{thm:inf}.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}

The correlation $\fC(d,r)$ contains a winning correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment to each variable of the equation.
Bob is asked to assign a value to a random variable of the chosen equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of $\ket{EPR}$,
the Magic square game can be won with certainty.
It has been shown that if a strategy can win this game almost perfectly, 
the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}.
So we say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain binary observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation \cite{coladan2017}.

@@

Following Slofstra's design, 
the sizes of the input alphabets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$ in $\LS(r)$.
%Restricting $r \leq 5$ as in \cref{thm:inf} implies that 
%$\LS(r)$ only uses constant-sized input and output alphabets.

The reason that we choose \cref{eq:uor} to be the relation enforced
by $\LS(r)$ is the following.
Winning $\LS(r)$ guarantees that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2
\end{align*}
with $U$ and $O$ satisfying \cref{eq:uor}.
%Then we can deduce that the eigenvalues of $O$ must be
%of the form $\omega_d^j = e^{i 2j\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root is $r$. 
Moreover, if we can certify that the unitary $O$
has the eigenvalue $\omega_d := e^{i 2\pi /d }$
where $r$ is a primitive root of $d$, \cref{eq:uor}
automatically guarantees that the spectrum of $O$ contains 
$\{ \omega_d^j \}_{j=1}^{d-1}$.
It also guarantees that the eigenspace of each distinct eigenvalue
has the same dimension. 
%We can also deduce that $U$ is a permutation of the eigenbasis of $O$.
%Winning this linear system game also guarantees that Alice and Bob share a state
%$\ket{\psi}$ such that 
% \begin{align*}
%     O \x O \ket{\psi} = \ket{\psi}, && 
%     U \x U \ket{\psi} = \ket{\psi}.
% \end{align*}
%From the equations above, we can deduce that
%$\ket{\psi}$ is spanned by tensor products of states in the eigenbasis of $O$,
%and is invariant under the permutation induced by $U$.

% The relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
% is spanned by tensor products of states in the eigenbasis of $O$.
% The relation $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
% under the permutation induced by $U$. 
%At this point, the eigenvalues of $O$ are unknown, so
%certifying the eigenvalues of $O$ requires another test.

@@

% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
%The difference between a nonlocal game and a nonlocal test will be discussed later.

The strong guarantee of \cref{eq:uor} is built on the assumption of an eigenvalue
of the unitary $O$, so the next problem is how to certify that $O$ has eigenvalue $\omega_d$.
In order to solve it, we design $\fC(d,r)$ to contain 
an extension of the optimal correlation 
that achieves the maximal violation of the weighted
CHSH inequality.
The $\alpha$-weighted CHSH inequality is defined by
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    \tM_1 = \pauliz && \tM_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    \tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && \tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $\tM_1, \tM_2$ and $\tN_1, \tN_2$ in \cref{sec:ext_chsh}.
Then we notice that 
\begin{align*}
    \tN_1\tN_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.

Therefore, in the extended correlation, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$ from a winning strategy of $\LS(r)$. Then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.
Combining this observation with the fact that $O$ satisfy the relation \cref{eq:uor},
we can conclude that all the eigenvalues of $O$ contains $\{ \omega_d^j \}_{j=1}^{d-1}$,
and the eigenspaces of all such eigenvalues have the same dimension.

%At this point, we have the explicit structure of $O$, so we 
%can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
%to prove the correlation $\fC(r, d)$ can robustly self-test 
%a maximally entangled state of dimension $4(d-1)$,
%\begin{align*}
%    \left(\frac{1}{\sqrt{d}} \sum_{j=1}^{d-1}\ket{j}\ket{d-j}\right)\x 
%    \ket{EPR}^{\x 2}.
%\end{align*}
%In this proof, we demonstrate a new way to apply the generalized swap-isometry
%proposed in \cite{yang2013} to robustly self-test a maximally entangled state of large local
%dimension.

The full correlation $\fC(r, d)$ is produced by an ideal strategy
that can win $\LS(r)$ perfectly and 
can reproduce the aforementioned extended correlation perfectly.
Combining the implications of a quantum strategy to win $\LS(r)$
and reproduce the extended correlation, we 
can prove that the correlation $\fC(r, d)$ can robustly self-test the state
$\ket{\tpsi}$ defined by
\begin{align*}
	\ket{\tpsi} = \frac{1}{\sqrt{d-1}} \left( \sum_{j=1}^{d-1} \ket{j}\ket{d-j} \right) \x \ket{EPR}^{\x 2}.
\end{align*}
More precisely, we prove that if some quantum strategy using the shared state
$\ket{\psi}$ can produce a correlation that is within trace distance
$\ep$ to $\fC(d,r)$, then there exist an local isometry
$\Phi_A \x \Phi_B$ and a state $\ket{junk}$ such that
\begin{align}
    \label{eq:distance}
    \norm{\Phi_A\x\Phi_B(\ket{\psi}) - \ket{junk}\x \ket{\tpsi}} = O(d^{5/2} r^d \ep^{1/8}).
\end{align}
Note that the isometry $\Phi_A \x \Phi_B$ only involves local operations
on Alice's and Bob's side.
The isometry $\Phi_A \x \Phi_B$ captures the essence of the generalized 
swap-isometry proposed in \cite{yang2013}, but it is constructed in a different way.

As mentioned at the start of this subsection, the last step of proving \cref{thm:inf} is to apply the general self-testing result of
$\fC(d,r)$ to the prime numbers with a primitive root $2$, $3$ or $5$.
The theorem follows naturally from the fact that there are infinitely many such
prime numbers \cite{murty1988}.

\subsection{Structure of the paper}
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:ext_chsh}. 
Then we give the correlation $\fC(d,r)$ and the ideal strategy to generate it in \cref{sec:full_test}.
\Cref{sec:main} is devoted to the robust self-testing proof. We end this paper with conclusions
in \cref{sec:conclu}.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations and mathematical background}
%-----------------------------------
%The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we self-test is denoted by
%\begin{align}
%\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
%\end{align}
%The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.

The EPR pair is denoted by 
\begin{align}
	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are denoted by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. 
Note that we only work with finite Hilbert spaces in our work.

@@

There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
\begin{definition}
    \label{def:spe_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let
    \begin{align*}
        \Gamma = \ip{\{s_i\}_{i \in [n]}  :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{ s_i s_j s_i = s_k\}_{(i,j,k)\in C}}.
    \end{align*}
    We say a group is a conjugacy group if it has a presentation of this form. 
\end{definition}
A conjugacy group is a special case of what Slofstra defined as 
a linear-plus-conjugacy group (Definition $26$ of \cite{slofstra2017}). 
The difference is that a conjugacy group does not have linear relations. 
The next definition follows the 
definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
\begin{definition}
    \label{def:nice_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let 
    \begin{align*}
        \Gamma = \ip{\{s_i\}_{i \in [n]} \cup \{s_{jk}\}_{(i,j,k)\in C} :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{s_{jk}^2 = e, s_is_js_i = s_k, s_{jk}s_js_k = e\}_{(i,j,k)\in C}}.
    \end{align*}
    We say a group is a nice conjugacy group if it has a presentation of this form. 
\end{definition}
The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
because
\begin{align*}
    [s_j, s_k] = s_js_ks_js_k = s_{jk}^2 = e.
\end{align*}
Next we give the definition of a group representation. 
\begin{definition}
    A representation of a group $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
\end{definition}
The last concept of group theory that we need is a group embedding.
\begin{definition}[Group embedding]
    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
\end{definition}
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. 
We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
for each $x \in \calX$. Similarly,
Bob's question set is denoted by $\calY$ and 
his family of answer sets is denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, 
and we follow this convention on Bob's side too.
The probability distribution over the questions of
a nonlocal game 
is given by a functions $\pi: \calX \times \calY \rightarrow [0,1]$,
A nonlocal game also comes with a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
the family of scoring functions.
Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the scoring function as 
$V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.

@@

%=============================
\section{Conclusions}
\label{sec:conclu}
%=============================
In summary, we identify a family of correlations with constant-sized input and output alphabets that can be used to robustly self-test
maximally entangled states with unbounded local dimension.
Before our work, the most efficient way 
was to use $O(\log d)$-sized input and $O(\log \log d)$-sized output alphabets to robustly self-test
the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.

Our result gives us deeper understandings of the set of quantum correlations.
In previous works that proved the non-closeness of the set of quantum correlations \cite{slofstra2017, slofstra2018}, 
lower bounds of the entanglement required to achieve certain correlations are identified.
We discover a large family of correlations such that we know exactly the entangled state
required to achieve each of the correlations in this family.
